A Comparison of Graph Processing Systems

### 2020-09-16 documentation/paper/sections/testingMethods.tex
used algorithms update

In detail, the algorithms for each framework are:
\begin{itemize}
	\item Galois: Galois supports all of our tested algorithms, with both a Push and a Pull variant for PageRank available. In the distributed scenario, there are Push and Pull versions for SSSP and BFS available as well.
	\item Gemini: \todo{}
	\item Giraph: Giraph does not natively supply a BFS algorithm, so in our comparisons a custom implementation is used. For SSSP, slight variations had to be made to the default implementation, to allow us to use different start vertices. For PageRank the supplied implementation is used.
	\item Ligra: \todo{}
	\item Polymer: Polymer suppoerts SSSP based on BellmanFord, BFS and two implementations of PageRank. The two implementations are a regular PR and a Delta Variant.
\end{itemize}

% \autoref{tbl:algorithms} shows the tested algorithms in detail.

% \newcommand{\txtdag}{\textsuperscript{\textdagger}}
% \newcommand{\singleNode}{\textsuperscript{s}}
% \newcommand{\distributed}{\textsuperscript{d}}
% \begin{table}
% 	\renewcommand{\arraystretch}{1.3}
% 	\centering
% 	\caption{REMOVE THIS // Tested Algorithms of Each Framework}
% 	\begin{tabularx}{0.9\columnwidth}{cYYYYY}
% 		\bf{Algorithm}&Galois&Gemini&Giraph&Ligra&Polymer\\\hline
% 		PageRank&Yes\singleNode{}, $\Delta$Push\distributed{}, $\Delta$Pull\distributed{}&&Yes\singleNode\distributed&&Regular\singleNode, $\Delta$\singleNode\\\hline
% 		SSSP&?, Push, Pull&&Yes\singleNode\distributed\txtdag&&Yes\singleNode{}\\\hline
% 		BFS&Yes&&Yes\singleNode\distributed{}*&&\\
% 		\hline
% 		\multicolumn{6}{p{0.5\columnwidth}}{* Algorithm not natively supported

% 		\txtdag{} Modified algorithm

% 		\distributed{} distributed

% 		\singleNode{} single-node}
% 	\end{tabularx}
% 	\label{tbl:algorithms}

% \end{table}

\subsection{Comparison of setup}

>>>>

In detail, the algorithms for each framework are:
\begin{itemize}
	\item Galois supports all of our tested algorithms, with both a Push and a Pull variant for PageRank available. In the distributed scenario, there are Push and Pull versions for SSSP and BFS available as well.
	\item Gemini \todo{}
	\item Giraph does not natively supply a BFS algorithm, so in our comparisons a custom implementation is used. For SSSP, slight variations had to be made to the default implementation, to allow us to use different start vertices. For PageRank the supplied implementation is used.
	\item Ligra \todo{}
	\item Polymer supports SSSP based on BellmanFord, BFS and two implementations of PageRank. The two implementations are a regular PR and a Delta Variant.
\end{itemize}
